Communication complexity: Chapter 7 \\ Multiparty communication

### 2019-03-15 CS860-CommunicationComplexity/assignments/Chapter7.tex
Problems 2 and 3

@@

@@

>>>>

\begin{proof}
Consider the protocol where player $1$ outputs $1$ if $x_2 = x_3 = \dots x_k$ and outputs $0$ otherwise. The protocol terminates with output $0$ in the latter case. In the former, player $2$ outputs $1$ if $x_1 = x_3$ and outputs $0$ otherwise, and these outputs correspond to the decision of the protocol in their respective cases.
\end{proof}

@@

\begin{proof}
We use the following identity which can be verified by case analysis
$$\Maj(x_i,y_i,z_i) = x_iy_i + y_iz_i + x_iz_i \mod 2.$$
Using this identity we see that
$$\MIP(x,y,z) = \bigoplus_{i\in[n]}\Maj(x_i,y_i,z_i) = \left(\bigoplus_{i\in [n]} x_iy_i\right)\oplus\left(\bigoplus_{i\in [n]} y_iz_i\right)\oplus\left(\bigoplus_{i\in [n]} x_iz_i\right).$$
On the right hand side, the first term can be computed by player $3$ and output, the second by player $1$, and the third by player $2$. With all $3$ bits anyone can then compute $\MIP(x,y,z)$.
\end{proof}

@@

\begin{proof}
